The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-06 paper.tex
update

  Motivated by these observations, we simulate three cases with different inclined angles,\
  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.

@@

  The bipolar jets are constantly ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.

  We resolve the jet source with the highest refinement level 11,\
  bringing the finest spatial resolution up to 0.4 pc.\

 \begin{enumerate}
    \item Why the overall structure is insensitive to jet direction?
      \begin{enumerate}
        \item Jet source size.
        \item Cold disk.
        \item Large pressure gradient along z-direction.
      \end{enumerate}
 \end{enumerate}

>>>>

  Motivated by these observations, we simulate the jet with an inclination angle\
  $45^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.

@@

  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time 1.2 Myr,\
  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

  The diameter and height of cylindrical source are 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
  much smaller than that of an individual clump by a factor of about 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.\
  Moreover, we resolve the jet source with the highest refinement level 11,\
  bringing the finest spatial resolution up to 0.4 pc.\
